FraCaS: 80 percent complete

### 2019-02-22 paper2018/paper.tex
background addition

\subsection{Dynamic Monadic Semantics}

>>>>

\subsection{Dynamic Monadic Semantics}
Dynamic Monadic Semantics have been proven to be an effective way of dealing with anaphora and ellipsis. There are a number of  approaches using monads or other similar ideas (e.g. continuations as in \cite{de2006}) for anaphora and ellipsis  \citet{Shan:2002,unger:2011,Barker:04,de2016,charlow:2017}. In this paper, we follow the approach  as described in \citet{bernardy_jolli}. More details on this will be given in the next section, where the actual system is presented.
